Spikes demo

### 2018-10-09 analysis/spikesdemo.Rmd
Added back signal plot to summarize.gaussian.sims.R.
Working on motorcycle .Rmd example.

This script illustrates key features of the SMASH method on a small,
simulated data set with heteroskedastic variances.

@@

This plot shows the "spikes" mean function (the black line),
+/- 2 standard deviations (the yellow lines), and
the simulated data (the blue points).

>>>>

This small demonstration illustrates key features of the SMASH method
on a small, simulated data set with heteroskedastic variances. This
code implements the example given in Sec. 4.1 of the paper.

@@

This plot shows the "spikes" mean function (the black line), +/- 2
standard deviations (the orange lines), and the simulated data (the
blue points).
